\textls[-0]{\thetitle}

### 2022-11-11 metatheory-condensed.tex
tweaks

\item
By contrast, $\wsig_{\texttt{tm}}$ is hidden from the typing of all other fields.
Their typing depends on the knowledge that \lsti!tm! has type~$\cU$,
rather than \TyS{\wcode{\wsig_{\texttt{tm}}}},
so they can be reused in a context where \lsti!tm! is defined as $\wcode{\wsig'_{\texttt{tm}}}$,
where $\wsig'_{\texttt{tm}}$ extends~$\wsig_{\texttt{tm}}$ with additional constructors.
%
For example, in \cref{fig:stlc-linkage-typing}, the typing of the case handlers of
\lsti{subst} (e.g., $t_6$) is oblivious to the definition of \lsti!tm!---it sees only $\text{\lsti!tm!}:\cU$---so
the case handlers can be reused by a linkage modeling \lsti{STLCFix}.

>>>>

\item
By contrast, $\wsig_{\texttt{tm}}$ is hidden from the typing of all other fields.
Their typing should depend on the knowledge that \lsti!tm! has type~$\cU$,
rather than \TyS{\wcode{\wsig_{\texttt{tm}}}},
so that they can be reused in a context where
\lsti!tm! is defined as $\wcode{\wsig'_{\texttt{tm}}}$,
where $\wsig'_{\texttt{tm}}$ extends~$\wsig_{\texttt{tm}}$ with additional constructors.
%
For example, in \cref{fig:stlc-linkage-typing}, the typing of the case handlers of
\lsti{subst} (e.g., $t_6$) is oblivious to the definition of \lsti!tm!---it sees only $\text{\lsti!tm!}:\cU$---so
the case handlers can be reused by a linkage modeling \lsti{STLCFix}.
